Why is time-to-resistance in mixtures influenced differently by effectiveness and exposure ?

### 2016-12-09 inst/documents/effectiveness_exposure_difference.Rmd
added abcd labs

#todo to get grid fig working.
#think about implementing in ggplot2 to make my life easier later ?
#although I'm not sure it would ?
#allow x axis labels and title to be removed
#add axis titles outside of the plot region
#remove curve legend on plots and put it somewhere else maybe on bottom
#? allow curves to be thicker

@@

#layout(matrix(1:4,2,2, byrow = TRUE))
#add lower panel for legend
#layout(matrix(c(1,2,3,4,5,5),3,2, byrow = TRUE), heights=c(1,1,0.5), respect=FALSE)

# layout( matrix(c(1,2,3,4,5,5),3,2, byrow = TRUE), heights=c(1,1,0.2), 
# respect=matrix(c(1,1,1,1,0,0),3,2, byrow = TRUE) )

#layout.show(n=5)

# layout( matrix(c(1:6,0,7,7,0,8,9),4,3, byrow = TRUE), heights=c(1,1,0.2,0.2), 
# respect=matrix(c(1,1,1,1,0,0),3,2, byrow = TRUE) )

layout( matrix(c(1:6,0,7,7,0,8,9),4,3, byrow = TRUE), heights=c(1,1,0.15,0.2), widths=c(0.1,1,1) )

@@

@@

@@

@@

>>>>

#todo to get grid fig working.
#think about implementing in ggplot2 to make my life easier later ?
#although I'm not sure it would ?

#? allow curves to be thicker

@@

#layout(matrix(1:4,2,2, byrow = TRUE))

#add lower panel for legend
#layout(matrix(c(1,2,3,4,5,5),3,2, byrow = TRUE), heights=c(1,1,0.5), respect=FALSE)

#layout( matrix(c(1,2,3,4,5,5),3,2, byrow = TRUE), heights=c(1,1,0.2), 
# respect=matrix(c(1,1,1,1,0,0),3,2, byrow = TRUE) )
#layout.show(n=5)

# add side panels for labels
layout( matrix(c(1:6,0,7,7,0,8,9),4,3, byrow = TRUE), heights=c(1,1,0.15,0.2), widths=c(0.1,1,1) )

@@

mtext('A)',side=3, adj=0, line=1, cex=0.9) #side=1b,2l,3t,4r

@@

mtext('B)',side=3, adj=0, line=1, cex=0.9) #side=1b,2l,3t,4r

@@

mtext('C)',side=3, adj=0, line=1, cex=0.9) #side=1b,2l,3t,4r

@@

mtext('D)',side=3, adj=0, line=1, cex=0.9) #side=1b,2l,3t,4r
